### 2020-11-20 pldi21/intro.tex
fix and make fig 3 fit

The tragedy is that these applications have 
limited support for abstraction and composition.
It is difficult, for example, to bind a
color to a variable for use in multiple locations in an
otherwise directly constructed game map,
or to define a function that computes portions of an 
otherwise directly constructed vector graphic,
or to transform a directly constructed musical sequence 
by passing it through a series of symbolically specified functions.
Moreover, it is difficult to add new affordances or to compose
affordances in ways that the application developer did not anticipate.
Users cannot easily make even simple changes like replacing a numeric text box in a color palette with a slider,
much less more ambitious changes like installing an alternative visual interface for expressing geospatial data queries in a workflow.

>>>>

The tragedy is that these applications have 
limited support for abstraction and composition.
It is difficult, for example, to bind a
color to a variable for use in multiple locations in an
otherwise directly constructed game map,
or to define a function that computes portions of an 
otherwise directly constructed vector graphic,
or to transform a directly constructed musical sequence 
by passing it through a series of symbolically defined functions.
Moreover, it is difficult to add new affordances or to compose
affordances in ways that the application developer did not anticipate.
Users cannot easily make even simple changes like replacing a numeric text box in a dialog with a slider,
much less more ambitious changes like installing an alternative visual interface for expressing geospatial data queries 
into a database frontend.

### 2020-11-20 pldi21/livelit-definitions.tex
fix and make fig 3 fit

\begin{figure}
\begin{lstlisting}
  type Color = (.r Int, .g Int, .b Int, .a Int)

  livelit $color at Color {
    capture { }

    type Model = (.r SpliceRef, .g SpliceRef, .b SpliceRef, .a SpliceRef)
    let init : UpdateMonad(Model) = do 
      r <- new_splice(`Int`, Some(`0`))
      g <- new_splice(`Int`, Some(`0`))
      b <- new_splice(`Int`, Some(`0`))
      a <- new_splice(`Int`, Some(`100`))
      return (r, g, b, a)

    type Action = 
    | ClickOnColor(Color)

    let view : Model -> ViewMonad(Html(Action)) = 
      fun model -> do 
        (* determine a color to display to the client, if possible *)
        r_res <- eval_splice(model.r)
        g_res <- eval_splice(model.g)
        b_res <- eval_splice(model.b)
        a_res <- eval_splice(model.a)
        let cur_color : Color = 
          case (r_res, g_res, b_res, a_res) 
          | (Some(Val(IntLit(r))), 
             Some(Val(IntLit(g))), 
             Some(Val(IntLit(b))), 
             Some(Val(IntLit(a)))) -> 
            Some((r, g, b, a))
          | _ -> None
        in

        r_editor <- editor(model.r, FixedWidth(20))
        g_editor <- editor(model.g, FixedWidth(20))
        b_editor <- editor(model.b, FixedWidth(20))
        a_editor <- editor(model.a, FixedWidth(20))

        (* ...render the UI using these splice editors... *)

    let update : Model -> Action -> UpdateMonad(Model) =
      fun model (ClickOnColor(r, g, b, a)) -> do 
        set_splice(model.r, IntLit(r))
        set_splice(model.g, IntLit(g))
        set_splice(model.b, IntLit(b))
        set_splice(model.a, IntLit(a))
        return (r, g, b, a)

    let expand : Model -> (Exp, List(SpliceRef)) = 
      fun model -> 
        (`fun r g b a -> (r, g, b, a)`, [model.r, model.g, model.b, model.a])
  }
\end{lstlisting}
\caption{Livelit Implementation: \li{\$color} (simplified for presentation)}
\label{fig:color-impl}
\end{figure}

>>>>

\begin{figure}
\begin{lstlisting}[xleftmargin=0.2cm,morekeywords={expansions,require}]
type Color = (.r Int, .g Int, .b Int, .a Int)

livelit $color at Color {
  type Model = (.r SpliceRef, .g SpliceRef, 
                .b SpliceRef, .a SpliceRef)

  let init : UpdateMonad(Model) = do 
    r <- new_splice(`Int`, Some(`0`))
    g <- new_splice(`Int`, Some(`0`))
    b <- new_splice(`Int`, Some(`0`))
    a <- new_splice(`Int`, Some(`100`))
    return (r, g, b, a)

  type Action = 
  | ClickOn(Color)

  let view : Model -> ViewMonad(Html(Action)) = 
    fun model -> do 
      (* determine a color to display *)
      r_res <- eval_splice(model.r)
      g_res <- eval_splice(model.g)
      b_res <- eval_splice(model.b)
      a_res <- eval_splice(model.a)
      let cur_color : Color = 
        case (r_res, g_res, b_res, a_res) 
        | (Some(Val(IntLit(r))), 
            Some(Val(IntLit(g))), 
            Some(Val(IntLit(b))), 
            Some(Val(IntLit(a)))) -> 
          Some((r, g, b, a))
        | _ -> 
          (* indetermine color shown as X *)
          None 
      in

      (* generate splice editors *)
      let size = FixedWidth(20) in 
      r_editor <- editor(model.r, size)
      g_editor <- editor(model.g, size)
      b_editor <- editor(model.b, size)
      a_editor <- editor(model.a, size)

      (* ... now we can render the UI ... *)

  let update : 
      Model -> Action -> UpdateMonad(Model) =
    fun model (ClickOn c) -> do 
      set_splice(model.r, IntLit(c.r))
      set_splice(model.g, IntLit(c.g))
      set_splice(model.b, IntLit(c.b))
      set_splice(model.a, IntLit(c.a))
      return model

  expansions require { }
  let expand : Model -> (Exp, List(SpliceRef)) = 
    fun model -> (`fun r g b a -> (r, g, b, a)`, 
      [model.r, model.g, model.b, model.a])
}
\end{lstlisting}
\vspace{-8px}
\caption{Livelit Implementation}
\label{fig:color-impl}
\end{figure}
